Frame Competition

### 2022-07-06 paper/Manuscript.Rmd
Fix plot display

@@

```{r afdmigration}
library(tidyverse)
library(here)
library(patchwork)
library(data.table)

@@

*Frame Competition Hypothesis: The more similar an medis's framing of an issue to a given parties' issue framing, the better that parties' electoral prospect.*

One key difference compared to other models of party competition, especially the one described in @Meguid2009 is that in the present model, party positions are considered fixed, while it is the media debate that moves. Large shifts in parties' issue positions are generally rare [@SOURCE], but the media debate is in permanent flux, promoting a constantly changing set of issues and related considerations to voters. While the classic model described in @Meguid2009 views parties' electoral performance as a function of parties position and issue salience, the present model views their electoral performance as a function of issue salience and the similarity of the dominant set of issue considerations to the set of considerations emphasised by the party to substantiate its position:

[insert formula]

@@

>>>>

```{r setup, include = F}

knitr::opts_chunk$set(echo = F, message = F, warning = F, cache = F, fig.height=6, fig.width=10, fig.align='center', eval = T)

library(tidyverse)
library(dplyr)
library(data.table)
library(patchwork)
library(here)

# load self-made functions
for (filename in list.files(here("code/functions"))){
  source(here(paste0('code/functions/', filename)))
}

@@

```{r afdmigration, fig.height = 10}

@@

*Frame Competition Hypothesis: The more similar the media's framing of an issue to a given parties' issue framing, the better that parties' electoral prospect.*

One key difference compared to other models of party competition, especially the one described in @Meguid2005 is that in the present model, party positions are considered fixed, while it is the media debate that moves. Large shifts in parties' issue positions are generally rare [@SOURCE], but the media debate is in permanent flux, promoting a constantly changing set of issues and related considerations to voters. Political actors sponsor frames and arguments, only some of which get to influence the debate. While the classic model described in @Meguid2005 views parties' electoral performance as a function of parties position and issue salience, the present model views their electoral performance as a function of issue salience and the similarity of the dominant set of issue considerations to the set of considerations emphasised by the party to substantiate its position.

@@

## Instrumenting Frame Attention
